Randomly select papers for review

### 2022-08-30 Writing/Randomisation/Randomise_Papers.Rmd
need to get some first-round results first to determine new methods

# Need seed set for reproducibility
set.seed(5378)

opts_knit$set(root.dir = "/Users/kelleherj/Documents/Research/QAEco/ODM_Review/dynamic-occupancy-model-review/")
```

Read in the excel sheets and process out the header
```{r Read-in excel sheets, echo = FALSE, message = FALSE, warning = FALSE}
# From the excel review spreadsheet, read in only the identifying characteristics 
identifierSheet <- readxl::read_xlsx("Review Spreadsheet.xlsx", 
                                     sheet = "Metadata", skip = 1) %>%
  # Drop rows prior to start of data
  slice(4:nrow(.)) %>%
  # Only need google search query and the ID reference
  select(Review_ID, Query = `Search terms`) 
# Repeat with the study metadata
studyDataSheet <- readxl::read_xlsx("Review Spreadsheet.xlsx", 
                                    sheet = "Study data", skip = 1) %>%
  # Cut out non-data rows
  slice(4:nrow(.)) %>%
  # Only need year data and ID reference
  select(Review_ID, Year) 
```

>>>>

# Need seed set for reproducibility
set.seed(5378)
```

Read in the excel sheets and process out the header
```{r Read-in excel sheets, echo = FALSE, message = FALSE, warning = FALSE}
# From the excel review spreadsheet, read in only the identifying characteristics 
identifierSheet <- readxl::read_xlsx("Data/Review Spreadsheet.xlsx", 
                                     sheet = "Metadata", skip = 1) %>%
  # Drop rows prior to start of data
  slice(4:nrow(.)) %>%
  # Only need google search query and the ID reference
  select(Review_ID, Query = `Search terms`) 
# Repeat with the study metadata
studyDataSheet <- readxl::read_xlsx("Data/Review Spreadsheet.xlsx", 
                                    sheet = "Study data", skip = 1) %>%
  # Cut out non-data rows
  slice(4:nrow(.)) %>%
  # Only need year data and ID reference
  select(Review_ID, Year) 
```
